---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, echo=FALSE}
library(TTR)
library(xts)
library(lmtest)
library(quantmod)
library(ggplot2)
```

```{r, echo=FALSE}
fileloc <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(fileloc)
rm(fileloc)
WorldMarkts99_20 <- readRDS("../Data/WorldMarkts99_20.RDS")
markets <- ls(WorldMarkts99_20)
View(WorldMarkts99_20)
```

```{r, echo=FALSE, warning=FALSE}
#retrieve_returns: Retrieve returns for a list of markets given a specified time period
#Variables -> period: ‘daily’, ‘weekly’, ‘monthly’, ‘quarterly’, ‘yearly’
#             type: arithmetic (discrete) or log (continuous)


#### 2001/07-2003/06
retrieve_returns <- function(sampling_per,type_c) {
  returns <- xts() #empty time series object
  for (i in seq_along(markets)){
    sym <- markets[i]
    daily_na <- na_interpolation(Ad(get(sym,envir = WorldMarkts99_20)),'linear')
    returns <- merge(returns,periodReturn(daily_na,period = sampling_per,type =type_c))
  }
  names(returns)<-markets
  return(returns)
}

method<-'log'
period<-'200107/200306'

daily_returns <- retrieve_returns('daily',method)
daily_returns <-daily_returns[period]

weekly_returns <- retrieve_returns('weekly',method)
weekly_returns <-weekly_returns[period]

monthly_returns <-retrieve_returns('monthly',method)
monthly_returns <- monthly_returns[period]

```

## Question 1

Note: The proof asked on the first part of this exercise can be found in the PDF attached to this Notebook.

A comparison between the arithmetic MA volatility and the EWMA volatility can be seen in the following image for the IBEX index during the 07/2001 - 06/2003 time period. \lambda was set to 0.94 for the EWMA. The results were computed for a 5 days rolling window.

```{r, echo=FALSE, warning=FALSE}
##Do the same analysis for volatilities series of each market
## Enough to consider the variance as  EMA of square returns
## Do the analysis for week and month sampling periods
## Optional: Apply  rolling windows with first year of data and step forward one period (week or month)

IBEX <-daily_returns$IBEX^2
arith_MA <- SMA(IBEX, n = 5)
ewma <- EMA(IBEX, n = 5, ratio = 0.06)

par(mfrow = c(1, 2))# space for one row of text at ticks and to separate plots
plot(arith_MA)
plot(ewma)

```

Notice how the plot on the right (EWMA volatility) presents a smoother behavior as it's more persistent than its counterpart (simple MA). This makes sense considering that in EWMA, past observations' contribution decay in a well behaved manner, whereas MA simply drops the past observation that falls outside the rolling window, causing more pronounced jumps in the resulting series. 






