---
title: "Homework 1-Part1_Gaussian"
output: html_notebook
---

```{r}
library(xts)
library(lmtest)
library(quantmod)
library(ggplot2)


## opciones para 
```

```{r}
directory = '~/Desktop/Master/Materias/Term 3/ML for Finance/Homeworks/Homework 1/Data/GoyalMonthly2005.csv'
sp500 = as.xts(read.zoo(directory,sep=',',header=TRUE, format='%Y-%m-%d'))
names(sp500)
mt=sp500['1927/2005']
```

Predict the SP500 with the financial indicators selected by
your team in the google spreadsheet (ep, dp, de, dy, dfy, bm, svar, ntis, infl, tbl , see
RLab3 GWcausalSP500.R), some lagged series of these indicators and lags of the target
using a GP regression with your desired kernel. Predict return, or price, or trend (for which
target works best?) select appropriate kernel and justify its use.(distance) correlation, VaR-test, Lasso ... (The script RLab3 GPlab.R can be of help. The
dataset is GoyalMonthly2005.csv and work within the period 1927/2005.)


```{r}
##compute log equity premium (GSPCep), 
## log returns of SP500 (logret)
logret =diff(log(mt$Index))
IndexDiv = mt$Index + mt$D12
#logretdiv <- log(IndexDiv) - log(mt$Index)
logretdiv =diff(log(IndexDiv))
logRfree = log(mt$Rfree + 1)
GSPCep <- logretdiv - logRfree
names(GSPCep) = "GSPCep"; 
#Target + Features: lags 1,2,3 of return and sqr rets
Z = merge(GSPCep,na.trim(lag(GSPCep,1)),na.trim(lag(GSPCep,2)),na.trim(lag(GSPCep,3)),
             na.trim(lag(GSPCep^2,1)),na.trim(lag(GSPCep^2,2)),
             #add other features here,
             all=FALSE)

#write.csv2(Z,file="GSPCep_data.csv")

##Predictor (wanna-be) variables
# dividend-price ratio (dp)
dp <- log(mt$D12) - log(mt$Index)
# dividend-payout ratio (de)
de <- log(mt$D12) - log(mt$E12)
# earnings to price
ep <- log(mt$E12) - log(mt$Index)
## dividend yield 
dy <- log(mt$D12) - log(lag(mt$Index,1))
# Default yield spread (dfy)= BAA-AAA rated corporate bond yields:
dfy <- mt$BAA -mt$AAA

## from the table consider stock variance (svar), Book-to-Market (b.m)
## net equity expansion (ntis, start 1926), inflation (infl)
# Treasury Bill rates (tbl, 1920)
svar = mt$svar
bm <-mt$b.m
ntis <- mt$ntis
infl <-mt$infl
tbl <- mt$tbl

names(GSPCep) = "GSPCep"; 
names(ep) = "ep"; names(bm) = "bm"   
names(dp) = "dp"; names(svar) = "svar"  
names(dy) = "dy"; names(de) = "de"   
names(ntis) = "ntis"; names(infl) = "infl"  
names(tbl) = "tbl"; names(dfy) ="dfy"  
```
 
```{r}
plot(GSPCep)
plot(GSPCep["1927/1931"])
plot(ep["1927/1931"])
```

### Causality Analysis to select meaningful variables
